Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-04 paper.qmd
Updated Figure 9

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = b_non_empty)) +
  geom_vline(xintercept = 0.12,
         linetype=2,
         color = "#bdbdbd",
         linewidth=1) +
  geom_hline(yintercept = 52,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = expression(m)) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = b_non_empty)) +
  geom_vline(xintercept = 0.12,
         linetype=2,
         color = "#bdbdbd",
         linewidth=1) +
  geom_hline(yintercept = 52,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(paste("binwidth (", a[1], ")")), y = expression(paste("non-empty bins (", m, ")"))) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())
